% This document provides the style to be used for a MSc Thesis at the
% Parallel and Distributed Systems group
\documentclass[11pt,twoside,a4paper,openright]{report}

% math packages
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage{amsthm}

% textblocks for title page
\usepackage[absolute]{textpos}

% use babel for proper hyphenation
\usepackage[british]{babel}

% Graphics: different for pdflatex or dvi output, choose one
%%\usepackage[dvips]{graphicx}
%%\usepackage[pdftex]{graphicx}
\usepackage{graphicx}

\usepackage{epstopdf}
\usepackage{rotating}
\usepackage{subfigure}

% FONT
\usepackage[scaled=.92]{helvet}
%\usepackage{times}

% for url's use "\url{http://www.google.com/}"
\usepackage{url}
\usepackage[plainpages=false]{hyperref} 
\usepackage{cleveref}



\usepackage{enumitem}

\usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes}


\usepackage{pifont}% http://ctan.org/pkg/pifont
\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%















\usepackage{tikz}
\usetikzlibrary{positioning,arrows}

\tikzset{
  block/.style={
    draw,
    rectangle,
    minimum height=1cm,
    minimum width=1cm,
    align=center
  },
  subblock/.style={
    draw,
    rectangle,
    minimum height=.75cm,
    minimum width=1.5cm,
    align=center
  },
  line/.style={->,>=latex},
  XOR/.style={draw,circle,append after command={
        [shorten >=\pgflinewidth, shorten <=\pgflinewidth,]
        (\tikzlastnode.north) edge (\tikzlastnode.south)
        (\tikzlastnode.east) edge (\tikzlastnode.west)
        }
    },
    LED/.style={draw,circle,append after command={
        [shorten >=\pgflinewidth, shorten <=\pgflinewidth,]
        %(\tikzlastnode.north) edge (\tikzlastnode.south)
        %(\tikzlastnode.east) edge (\tikzlastnode.west)
        }
    },
  dot/.style={draw,circle,minimum size=2mm,inner sep=0pt,outer sep=0pt,fill=black},
}




















% Information that will be filled in at various points in the report
\newcommand{\reportTitle}{Leveraging VLC for energy disaggregation in Smart Buildings}
\newcommand{\reportAuthor}{Johnny Verhoeff}
\newcommand{\reportEmail}{j.s.c.j.verhoeff@student.tudelft.nl}
\newcommand{\reportUrlEmail}{\href{mailto:\reportEmail}{\reportEmail}}
\newcommand{\reportMSC}{Embedded Systems} %{Embedded Systems}{Computer Engineering}{Computer Science}{Electrical Engineering}
\newcommand{\reportDate}{\today} %TODO: Dit is de datum van uitgifte van final versie aan de afstudeer commissie 
\newcommand{\presentationDate}{24th October 2016} %TODO: Dit is de datum van de afstudeerpresentatie 
\newcommand{\graduationCommittee}{

Chair: Prof. dr. K.G. Langendoen, Faculty EEMCS, TU Delft \\
Committee member: dr. ir. L.M. Ramirez Elizondo, Faculty DCE\&S, TU Delft \\ 
Committee member: dr. ir. M.A. Z\'u\~niga Zamalloa, Faculty EEMCS, TU Delft \\


} 

\newcommand{\reportAbstract}{
  
Energy consumption is an ever pressing issue.
Therefor it is needed to know what that energy is being used for.
Smart-meters can already disaggregate home appliances by looking at the distinct energy signatures of appliances.
But other items such as lighting has not been successful yet in disaggregating on a per lamp basis, due to the similar energy signatures lighting has.
In this work IDs are assigned to lights which are transmitted by the light via VLC.
The modulation of the ID will also propagate through the current that the lights draw.
To this purpose coding sequences were investigated that would allow for disaggregation of these lights by looking at the aggregated energy use, so that individual lights can be identified as being on or off.
With piggybacking on VLC, each light will get a unique ID, that they can transmit via VLC and the same ID will also be transmitted through the power they draw due to the modulation.
Hardware was designed, specifically to let that ID map into the energy signature.
And experiments were performed with commercial LEDs.
With a setup of multiple LEDs, each LED could be successfully identified as being on or off, in both DC and AC environments.
Furthermore, simulations have been performed in order to show the scalability of the proposed method.
And multiple items are highlighted that could be improved or otherwise investigated.













}
%\newcommand{\reportKeywords}{TODO KEYWORDS}

% For pdflatex
\pdfinfo{
   /Author (\reportAuthor)
   /Title  (\reportTitle)
   %/Keywords (\reportKeywords)
}

\begin{document}

\pagenumbering{alph}
\pagestyle{empty}





\renewcommand*{\chapterautorefname}{Chapter}




% FRONTCOVER
\include{template/frontcover}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\hoffset=1.63cm
\oddsidemargin=0in
\evensidemargin=0in
\textwidth=5in

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\parindent=1em

% EMPTY PAGE
\cleardoublepage

\pagestyle{plain}
\pagenumbering{roman}
\setcounter{page}{1}

% TITLE PAGE: page i (hidden)
\include{template/titlepage}

% GRADUATION DATA AND ABSTRACT: pages ii and iii (hidden)
\include{template/graduationdata}
%\setcounter{page}{4}

% EMPTY PAGE: page iv
\cleardoublepage

% OPTIONAL QUOTATION: page v
%\include{quotation}
% EMPTY PAGE: page vi
%\cleardoublepage

% PREFACE: page v
\include{chapters/preface}
% EMPTY PAGE: page vi
\cleardoublepage

% TABLE OF CONTENTS: starting at page vii
\tableofcontents

\cleardoublepage

\pagenumbering{arabic}
\setcounter{page}{1}


\setlength{\parskip}{\baselineskip}%
%\setlength{\parindent}{0pt}%


% INTRODUCTION: page 1
\include{chapters/introduction-chapters/introduction}

\include{chapters/related-work-chapters/related-work}

\include{chapters/design-requirements-chapters/design-requirements}

\include{chapters/cdma-chapters/cdma}

\include{chapters/hardware-chapters/hardware-design}

\include{chapters/evaluation-chapters/evaluation}





% CONCLUSIONS AND FUTURE WORK
\include{chapters/conclusionsandfuturework}

% BIBLIOGRAPHY
%#define SORTED 1
\bibliographystyle{bib/latex8}
\bibliography{bib/mycollection}

\appendix


\include{chapters/appendix/dc-test-bed/dc-test-bed-schematic}

\include{chapters/appendix/commercial-230v-ac-modified-schematic/commercial-230v-ac-modified-schematic}

\include{chapters/appendix/custom-modulator/custom-modulator}

\include{chapters/appendix/custom-current-sampler/custom-current-sampler}







\end{document}

