% !TeX root = ../../../thesis.tex

\section{Hardware}
\label{sec:hardware-evaluation}

The following two sections will describe the evaluation of the designed hardware and software, first for the DC testbed and then the AC testbed.
All LEDs will be assigned an ID that has the same length.
As discussed in \autoref{chp:cdma}, the correlation calculations only hold when CDMA codes are used from the same set.
The ID is programmed in the micro-controller before they are installed in their position in a room.
Based on the length of this ID, a certain amount of LEDs are supported, which is explained in \autoref{sec:interference-solution}.
But when the number of lights in the building increases, the new total number of lights may exceed the supported number of lights by the length of the IDs that were already assigned to each light.
When this happens all the IDs must be changed to another ID of a different length that does support the new amount of lights.
This may be done via a photo-diode as a receiver for each light, to receive the new ID.
In this way each light can be used again, even when the total number of lights increases.


In the following evaluation sections, all attached LEDs will be modulating with a different ID per LED.
This represents the worst case: Every LED is modulating and thereby causing interference.
Since every LED will be modulating we can evaluate if the state of the LEDs can indeed be identified as being on.
If this is not the case, this will be classified as a false-negative.
But for completeness we must also evaluate what happens when the system tries to identify an ID which corresponds to an LED that is off.
For this reason, an extra ID will be used to represent an LED in an off state.
The raw ADC signal will be showed as well as the steps that are required in order to process the raw data such that the correlation calculations can be performed.
Next, the correlation graph will be showed for an ID that is being used to modulate one of the LEDs as well as the correlation graph for the extra ID which represents an LED in an off state. 
Finally the F-measure will be showed for these correlation graphs.









\input{chapters/evaluation-chapters/hardware/dc/dc-evaluation}

\input{chapters/evaluation-chapters/hardware/ac/ac-evaluation}